Analysis of Bauer et al. (unpublished) Field experiment: <br> Persistence

### 2022-12-07 R/model_recovery_check.Rmd
Update model_recovery_check.Rmd

```{r load-models collapse = TRUE, message = FALSE}
load(file = here("outputs", "models", "model_recovery_full.Rdata"))
load(file = here("outputs", "models", "model_recovery_full_prior.Rdata"))
# BARG 1.E
#load(file = here("outputs", "models", "model_recovery_2_prior.Rdata"))
# BARG 5.A/B/C
#load(file = here("outputs", "models", "model_recovery_2_flat.Rdata"))
m_1 <- m_full
m_2 <- mfull_prior
```

@@

```{r write-csv echo = FALSE}
write.csv(draws1, here("outputs", "statistics", "table_recovery.csv"))
```

>>>>

```{r load-models, collapse = TRUE, message = FALSE}
load(file = here("outputs", "models", "model_recovery_full.Rdata"))
load(file = here("outputs", "models", "model_recovery_full_prior.Rdata"))
# BARG 1.E
#load(file = here("outputs", "models", "model_recovery_2_prior.Rdata"))
# BARG 5.A/B/C
#load(file = here("outputs", "models", "model_recovery_2_flat.Rdata"))
m_1 <- m_full
m_2 <- mfull_prior
```

@@

```{r write-csv, echo = FALSE}
write.csv(draws1, here("outputs", "statistics", "table_recovery.csv"))
```
